### 2021-04-14 paper.Rmd
minor fixes

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot. (Adapted from E.-K. Lee et al. 2005, Figure 1.) }
\label{fig:notation-huber}
\end{figure*}

@@

<!-- SL: I think this paragraph could moved down to the bottom of this section -->
Various displays are available to show projections in 1-$d$, 2-$d$ and higher dimensions. A 1-$d$ projection displays the data in a histogram analogous to a shadow puppet being projected onto a wall, while 2-$d$ projections are displayed as scatterplots. Higher dimensional projections can be shown with multivariate displays like SPLOMs or parallel coordinates. Figure \ref{fig:display} shows a variety of displays for projections and these displays are useful to show the non-normal distributions in the projected data, clustering structure, and multivariate relationship between variables.

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot. (Adapted from Lee et al. 2005, Figure 1.) }
\label{fig:notation-huber}
\end{figure*}

@@

<!-- SL: I think this paragraph could moved down to the bottom of this section -->
Various displays are available to show projections in 1D, 2D and higher dimensions. A 1D projection displays the data in a histogram analogous to a shadow puppet being projected onto a wall, while 2D projections are displayed as scatterplots. Higher dimensional projections can be shown with multivariate displays like SPLOMs or parallel coordinates. Figure \ref{fig:display} shows a variety of displays for projections and these displays are useful to show the non-normal distributions in the projected data, clustering structure, and multivariate relationship between variables.
